Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement

### 2013-12-19 Tex/paper/methods.tex
Metropolis entfernt

The results are obtained through Monte Carlo simulations.
For each sweep \(N\) single spin flip Metropolis updates, one
Wolff cluster update and one parallel tempering swap are
performed. These algorithms will be outlined short in the following.\\
Because it is not known before, where the critical temperatures
\(T_c\) are located, the Wolff cluster algorithm is used for
every temperature. Albeit the efficiency of the algorithmic procedure
was not dissected for every temperature, the speed up
near criticality should be worth the moderate slow down at other temperatures.

\subsection{Single Spin Flip Metropolis Update}
    A \emph{Metropolis} Monte Carlo \cite{Metropolis1953} simulation of an
    Ising model will choose a random spin, calculate the energy change
    \begin{equation}
        \Delta H = H_\nu - H_\mu
        \label{eq:dH}
    \end{equation}
    that would result from a flip of that spin. Where \(\mu\) is the
    state before the flip and \(\nu\) after the flip. The flip is then executed
    with the probability
    \begin{equation}
        A(\mu \to \nu) =
        \begin{cases}
            1                            & \Delta H \le 0 \\
            \exp{\brac{-\beta \Delta H}} & \Delta H > 0
        \end{cases}.
        \label{eq:metropolis}
    \end{equation}
    see Refs.\ \cite{NewmanBarkema1999} \cite{Katzgraber2011}.
    So if a transition lowers the energy it will be always done. This
    results in a high ratio between flipped spins and chosen spins.
    Therefore it minimizes the calculations needed for a change of
    the state. Also note that \(\Delta H\) is easy to calculate,
    because it is only affected by the spin of the neighbors of the
    chosen site.

>>>>

The results are obtained through Monte Carlo simulations.
For each sweep \(N\) single spin flip Metropolis updates \cite{Metropolis1953}, one
Wolff cluster update \cite{Wolff1989} and one parallel tempering swap \cite{ParallelTempering1986} are
performed. The latter two algorithms will be outlined short in the following.\\
Because it is not known before, where the critical temperatures
\(T_c\) are located, the Wolff cluster algorithm is used for
every temperature. Albeit the efficiency of the algorithmic procedure
was not dissected for every temperature, the speed up
near criticality should be worth the moderate slow down at other temperatures.
